### 2025-01-29 paper/preprint/paper.tex
vamos

@@

@@

@@

  \textbf{Obj.} & \textbf{\$\textbackslash{}lambda\$ (exper)} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule

@@

@@

>>>>

\subsection{Training Details}\label{training-details}

@@

For the initial round of experiments we

@@

\begin{itemize}
\tightlist
\item
  \textbf{Energy Penalty} (Table~\ref{tbl-lin_sep-lambda_energy_exper}):
  \emph{ECCo} generally does yield better results than \emph{Vanilla}
  for higher choices of the energy penalty (10,15) during training.
  \emph{Generic} performs poorly accross the board. \emph{Omni} seems to
  have an anchoring effect, in that it never performs terribly but also
  never as good as the best \emph{ECCo} results. \emph{REVISE} performs
  poorly across the board.
\item
  \textbf{Cost (distance penalty)}: Results for all generators (except
  \emph{Omni}) are quite bad, which can likely be attributed to
  extremely bad results for some choices of the \textbf{Energy Penalty}
  (results here are averaged). For \emph{ECCo} and \emph{Generic},
  higher cost values generally lead to worse results.
\item
  \textbf{Maximum Iterations}: No clear patterns recognizable, so it
  seems that smaller choices are ok.
\item
  \textbf{Validity}: \emph{ECCo} almost always valid except for very low
  values during training and high values at evaluation time.
  \emph{Generic} often has poor validity.
\item
  \textbf{Accuracy}: Seems largely unaffected.
\end{itemize}

@@

  \textbf{Objective} & \textbf{$\lambda_{\text{div}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule

@@

\begin{itemize}
\tightlist
\item
  \textbf{Energy Penalty} (Table~\ref{tbl-moons-lambda_energy_exper}):
  \emph{ECCo} consistently yields better results than \emph{Vanilla},
  except for very low choices of the energy penalty during training for
  which it performs abismal. \emph{Generic} performs quite badly across
  the board for high enough choices of the energy penalty at evaluation
  time. \emph{Omni} has small positive effect. \emph{REVISE} performs
  poorly across the board.
\item
  \textbf{Cost (distance penalty)}: \emph{Generic} generally does better
  for higher values, while \emph{ECCo} does better for lower values.
\item
  \textbf{Maximum Iterations}: No clear patterns recognizable, so it
  seems that smaller choices are ok.
\item
  \textbf{Validity}: \emph{ECCo} generally achieves full validity except
  for very low choices the energy penalty during training and high
  choices at evaluation time. \emph{Generic} performs poorly for high
  choices of the energy penalty during evaluation.
\item
  \textbf{Accuracy}: Largely unaffected although \emph{ECCo} suffers a
  bit for very low choices the energy penalty during training.
  \emph{REVISE} suffers a lot in general (around 10 percentage points).
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Energy Penalty} (Table~\ref{tbl-circles-lambda_energy_exper}):
  \emph{ECCo} consistently yields better results than \emph{Vanilla},
  though primarily for low to medium choices of the energy penalty
  (\textless=5) during training. The same goes for \emph{Generic}, which
  sometimes outperforms \emph{ECCo} (for small energy penalty at
  evaluation time). \emph{Omni} does alright for lower energy penalty at
  evaluation time, but loses out for higher choices. \emph{REVISE}
  performs poorly across the board (except very low choices at
  evaluation time).
\item
  \textbf{Cost (distance penalty)}: \emph{ECCo} and \emph{Generic}
  generally achieve the best results when no cost penalty is used during
  training. Both \emph{Omni} and \emph{REVISE} are largely unaffected.
\item
  \textbf{Maximum Iterations}: \emph{ECCo} consistently yields better
  results for higher numbers of iterations. \emph{Generic} generally
  does best for a medium number (50). \emph{Omni} is sometimes invalid
  (\textbf{???}).
\item
  \textbf{Validity}: \emph{ECCo} tends to outperform its \emph{Vanilla}
  counterpart, though primarily for low to medium choices of the energy
  penalty (\textless=5) during training and evaluation. \emph{Vanilla}
  typically worse across the board.
\item
  \textbf{Accuracy}: Mostly unaffected, but \emph{REVISE} again
  consistently some deterioration and \emph{ECCo} deteriorates for high
  choices of energy penalty during training, reflecting other outcomes
  above.
\end{itemize}

### 2025-01-29 paper/sections/appendix.qmd
vamos

@@

```{julia}
results_dir = ENV["INITIAL_RUN"]
```

@@

@@

@@

@@

>>>>

## Training Details

@@

```{julia}
results_dir = ENV["INITIAL_RUN_RESULTS"]
config_dir = ENV["INITIAL_RUN_CONFIG"]
```

For the initial round of experiments we

@@

```{julia}
dict = CTExperiments.from_toml(joinpath(config_dir,"gen_params.toml")) 
```

@@

- **Energy Penalty** (@tbl-lin_sep-lambda_energy_exper): *ECCo* generally does yield better results than *Vanilla* for higher choices of the energy penalty (10,15) during training. *Generic* performs poorly accross the board. *Omni* seems to have an anchoring effect, in that it never performs terribly but also never as good as the best *ECCo* results. *REVISE* performs poorly across the board.
- **Cost (distance penalty)**: Results for all generators (except *Omni*) are quite bad, which can likely be attributed to extremely bad results for some choices of the **Energy Penalty** (results here are averaged). For *ECCo* and *Generic*, higher cost values generally lead to worse results.
- **Maximum Iterations**: No clear patterns recognizable, so it seems that smaller choices are ok. 
- **Validity**: *ECCo* almost always valid except for very low values during training and high values at evaluation time. *Generic* often has poor validity.
- **Accuracy**: Seems largely unaffected.

@@

- **Energy Penalty** (@tbl-moons-lambda_energy_exper): *ECCo* consistently yields better results than *Vanilla*, except for very low choices of the energy penalty during training for which it performs abismal. *Generic* performs quite badly across the board for high enough choices of the energy penalty at evaluation time. *Omni* has small positive effect. *REVISE* performs poorly across the board.
- **Cost (distance penalty)**: *Generic* generally does better for higher values, while *ECCo* does better for lower values.
- **Maximum Iterations**: No clear patterns recognizable, so it seems that smaller choices are ok. 
- **Validity**: *ECCo* generally achieves full validity except for very low choices the energy penalty during training and high choices at evaluation time. *Generic* performs poorly for high choices of the energy penalty during evaluation.
- **Accuracy**: Largely unaffected although *ECCo* suffers a bit for very low choices the energy penalty during training. *REVISE* suffers a lot in general (around 10 percentage points).

@@

- **Energy Penalty** (@tbl-circles-lambda_energy_exper): *ECCo* consistently yields better results than *Vanilla*, though primarily for low to medium choices of the energy penalty (<=5) during training. The same goes for *Generic*, which sometimes outperforms *ECCo* (for small energy penalty at evaluation time). *Omni* does alright for lower energy penalty at evaluation time, but loses out for higher choices. *REVISE* performs poorly across the board (except very low choices at evaluation time).
- **Cost (distance penalty)**: *ECCo* and *Generic* generally achieve the best results when no cost penalty is used during training. Both *Omni* and *REVISE* are largely unaffected.
- **Maximum Iterations**: *ECCo* consistently yields better results for higher numbers of iterations. *Generic* generally does best for a medium number (50). *Omni* is sometimes invalid (**???**).
- **Validity**: *ECCo* tends to outperform its *Vanilla* counterpart, though primarily for low to medium choices of the energy penalty (<=5) during training and evaluation. *Vanilla* typically worse across the board.
- **Accuracy**: Mostly unaffected, but *REVISE* again consistently some deterioration and *ECCo* deteriorates for high choices of energy penalty during training, reflecting other outcomes above.
